Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
more prog synthesis comments implemented

\paragraph{General architecture of the program synthesiser}
%
\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
that is updated incrementally.
Given a specification $\sigma$ over variables $x$
and $P$, the {\sc synth} procedure tries to find an existential witness $P$
that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
%
$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$

If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to {\sc verify}, which determines whether it does satisfy
the specification on all inputs by checking satisfiability of the following 
verification formula:
%
$\exists x . \lnot \sigma(x, P)$

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates. 
Otherwise, the witness $x$ is an input on which the candidate solution fails
to meet the specification.  This witness $x$ is added to the {\sc inputs}
set, and the loop iterates again.  It is worth noting that each iteration of the
loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  If
the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and we get a new counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02644824981689453125\\
\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
\end{array}
$$
\blue{[Nice, now I'm in the groove. Next unfolds well.] }
After adding this new counterexample to the set of {\sc inputs}, in the 
next {\sc synthesise} phase, we get a new candidate solution that holds
for both uncertainties in {\sc Inputs}:

>>>>

\paragraph{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the form
$\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs} . \sigma(\vec{x}, \vec{P})$
where $\vec{P}$ ranges over functions, $\vec{x}$ ranges over
ground terms and $\sigma$ is a quantifier-free formula.
We interpret the gound terms over some finite domain $\mathcal{D}$.

The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
that is updated incrementally.
Given the aforementioned specification $\sigma$, the {\sc synth} procedure 
tries to find an existential witness $P$
that satisfies the specification $\sigma(x, P)$ for all $x$.
%
If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to {\sc verify}, which determines whether it does satisfy
the specification on all inputs by checking satisfiability of the following 
verification formula:
%
$\exists x . \lnot \sigma(x, P)$

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates. 
Otherwise, the witness $x$ is an input on which the candidate solution fails
to meet the specification.  This witness $x$ is added to the {\sc inputs}
set, and the loop iterates again.  It is worth noting that each iteration of the
loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  
Given that the full set of inputs $\mathcal{D}$ 
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and we get a new counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02644824981689453125\\
\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
After adding this new counterexample to the set of {\sc inputs}, in the 
next {\sc synthesise} phase, we get a new candidate solution that holds
for both uncertainties in {\sc Inputs}:
